\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
new pics vel magn

In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields as the presence of this extra inlet increases the flow at the top layers.

@@

>>>>

In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers.

@@

\begin{figure}
\centering 
%\begin{minipage}{1.0\textwidth}%
%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.png}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.png}%
%\end{minipage}%
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. Reading from top to bottom, the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh (middle) and finally the velocity magnitude for adaptive mesh with double inlet (bottom) is compard. The main difference between the top plot and the middle one is the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns. While there is a significant difference between the top and middle plot, at the bottom one, the impact of a second injection interval can be seen from the slope and the rate that the velocity magnitude is changing. }
\label{fig:vel_magn}
\end{figure}
